---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# SticsRtests

A package to make integration tests for the SticsRPacks packages

---

<!-- badges: start -->
[![Travis build status](https://travis-ci.org/SticsRPacks/SticsRTests.svg?branch=master)](https://travis-ci.org/SticsRPacks/SticsRTests)
<!-- badges: end -->

This package is used to test the functions from all the distributed R packages from SticsRPacks for tests that cannot be integrated directly in the packages because they have to use external programs such as STICS or JavaSTICS (not distributed freely).

The package uses the `testthat` package to make all tests, a version of JavaSTICS and STICS from an always up-to-date google drive, and the [data repository](https://github.com/SticsRPacks/data) from the SticsRPacks organisation.

To test the packages functions all at once, simply press `ctrl+shift+T`, or execute this command in the R console:

```{r eval=FALSE}
testthat::test_package()
```

## Useage

To use this package, follow these steps: 

* clone it from Github (https://github.com/SticsRPacks/data.git);  

* download JavaSTICS and place it at the root of the package, with the name of type "JavaSTICS-v85" (for version 8.5 here);  

* download the data by executing these commands in the R console: 

```{r eval=FALSE}
data_dir= file.path(getwd(),"data")
dir.create(data_dir)
data_dir_zip= normalizePath(file.path(data_dir,"master.zip"), winslash = "/", mustWork = FALSE)
download.file("https://github.com/SticsRPacks/data/archive/master.zip", data_dir_zip)
unzip(data_dir_zip, exdir = data_dir)
unlink(data_dir_zip)
```

The data is now in the data folder, folder "data-master". For exemple the data `study_case_1` for the version 9 of the model is located at: 

```{r}
data_dir= file.path("data-master","study_case_1","V9.0")
data_dir
```

## Further information

For more information about unit testing, please read [this vignette](https://sticsrpacks.github.io/sandbox/articles/make-a-package.html#test-your-functions) in the `sandbox project`.
